Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-07-15 doc/PRF2022/PRF_main.tex
small changes to paper

To determine $\FF_i$ and $T_i$, the particles minimize the free energy
\begin{equation}
\label{eq:free_energy}
F = \gamma
\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
\end{equation}
Here, $u(\xx,t)$ is an order parameter for the structure of water,
$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
We model water structure
using the screened Laplace equation boundary value problem:
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ gives the degree of hydrophobicity
the particle-solvent interface (Figure~\ref{fig:bcs}).

@@

We use the parameters $\mu = 1$ cP, $\gamma = 4$ pN nm$^{-1}$,
$\rho = 5$ nm, $c = 1.25$ nm, $M = 2$ pN, and $\rho_0 = 0.5$ nm.
\subsection{Boundary integral represenation and time stepping}
We recast \eqref{eq:stokes}-\eqref{eq:rigid-vel} and \eqref{eq:SL}
as boundary integral equations (BIEs) and discretize each BIE at
$N$ points on each of the $N_b$ particles with a collocation method.
To express the solution of \eqref{eq:SL},
we adopt the double layer potential
\begin{align}
\label{eq:SL_BIE}
u({\bf x}) = \DD[\sigma](\xx) = \int_\Gamma \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, \dif s_\yy
, \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL},
$K_0$ is the zeroth-order modified Bessel function of the first kind,
and $\sigma$ is a scalar-valued density function.
The subscript in $\dif s_\yy$ denotes integration with respect to $\yy \in \Gamma$. 
For the velocity, we use the representation [REF]
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
\end{align}
with the vector-valued density function $\eeta$,
Stokeslet 
$\SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} + \frac{\rr \otimes \rr}{|\rr|^2}\right)$,
and Rotlet
$\RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}$,
$\rr = \xx - \aa_i$ [REF].

@@

The translational and angular velocities guarantee that the fluid forces
balanace the imposed forces. The imposed forces include the hydrophobic
interactions that arise so that particles minimize the free energy of
the structure of the surronding water molecules. The free energy
functional is
\begin{align}
\label{eq:free_energy}
  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
  \,d\xx,
\end{align}
where $u$ is an order parameter for the structure of water, $\rho$ is a
decay length, $C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds which is
much smaller than characteristic time for particle motion.
%\cite{MaGa13}. 
Thus we assume $u$ minimizes $F[u]$ for all times. Assuming appropriate
conditions on $f(u)$,
% (\cite{evans10}, \S 8.2),
$u$ satisfies the Euler-Lagrange equation
\begin{alignat}{3}
  \label{eq:SL}
  -\rho^2 \Delta u + \tfrac{1}{2}f'(u) &= 0, && \xx \in \Omega, \\
  u &= g, && \xx \in \bd\Omega, \\
  u &\rightarrow 0, \qquad&& |\xx| \rightarrow \infty.
\end{alignat}
Equation~\eqref{eq:SL} is solved with a boundary integral equation
method. The boundary condition $g$ is a material label that is
transported with the particle (Figure~\ref{fig:bcs}).

@@

Distinct morphologies can be obtained from 
the HAP model by shifting the boundary condition $g(\xx)$.
Consider the linear case where $f(u) = u^2$.
This choice makes \eqref{eq:SL} a boundary value
problem for the screened-Laplace equation
and the solutions have a boundary layer structure that decays to $0$ in the
bulk with the decay length $\rho$.
We consider three kinds of boundary conditions
on particle $\Gamma_i$:
\begin{equation}
  \label{eq:bcs}
  \begin{tabular}{c|c|c}
     \text{(i)} & \text{(ii)} & \text{(iii)} \\
    \hline
    \rule{0pt}{4ex} 
      $g(\mathbf{x}) = \displaystyle \frac{1+\cos (\theta_i(\xx))}{\sqrt{3\pi r}}$
    & $g(\mathbf{x}) = \displaystyle \frac{2+\cos (\theta_i(\xx))}{\sqrt{9\pi r}}$
    & $g(\mathbf{x}) = \displaystyle \frac{\cos (\theta_i(\xx))}{\sqrt{\pi r}}$
\end{tabular}
\end{equation}
  The number $\theta_i(\xx)$ is the angle formed by the position $\xx$, the
particle center $\aa_i$, and the particle director $\dd_i$.% (Figure \ref{fig:flow_map}).
The normalizations e.g., $(\pi r)^{-1/2}$, provide a uniform
surface energy $\int_{\Gamma_i} g^2 \,ds = 1$ for circular particles
of radius $r$. 
The cases (ii) and (iii) are obtained by applying a vertical shift
and scaling to case (i), see Figure~\ref{fig:bcs}.
Using this setup, we simulate the dynamics of 60 particles with one set of random
initial positions and orientations as shown in Figure~\ref{fig:relax}(a)

>>>>

To determine $\FF_i$ and $T_i$, the particles minimize the free energy
\begin{equation}
\label{eq:free_energy}
F = \gamma
\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
\end{equation}
Here, $u(\xx,t)$ is an order parameter for the structure of water,
$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
We model water structure
using the screened Laplace equation boundary value problem:
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ gives the degree of hydrophobicity the
particle-solvent interface.

@@

We use the parameters $\mu = 1$ cP, $\gamma = 4$ pN nm$^{-1}$,
$\rho = 5$ nm, $c = 1.25$ nm, $M = 2$ pN, and $\rho_0 = 0.5$ nm.

\subsection{Boundary integral represenation and time stepping}
We recast \eqref{eq:stokes}--\eqref{eq:rigid-vel} and \eqref{eq:SL}
as boundary integral equations (BIEs) and discretize each BIE at
$N$ points on each of the $N_b$ particles with a collocation method.
To express the solution of \eqref{eq:SL},
we adopt the double layer potential
\begin{align}
\label{eq:SL_BIE}
u({\bf x}) = \DD[\sigma](\xx) = \int_\Gamma \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, \dif s_\yy
, \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL},
$K_0$ is the zeroth-order modified Bessel function of the first kind,
and $\sigma$ is a scalar-valued density function.
The subscript in $\dif s_\yy$ denotes integration with respect to $\yy \in \Gamma$. 
For the velocity, we use the representation [REF]
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
\end{align}
with the vector-valued density function $\eeta$,
Stokeslet 
$\SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} + \frac{\rr \otimes \rr}{|\rr|^2}\right)$,
and Rotlet
$\RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}$,
$\rr = \xx - \aa_i$ [REF].

@@

The translational and angular velocities guarantee that the fluid forces
balanace the imposed forces. The imposed forces include the hydrophobic
interactions that arise so that particles minimize the free energy of
the structure of the surronding water molecules. The free energy
functional is
\begin{align}
\label{eq:free_energy}
  F[u] = C \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} f(u)\right)
  \,d\xx,
\end{align}
where $u$ is an order parameter for the structure of water, $\rho$ is a
decay length, $C$ is a constant, and $f(u)$ is a potential.
Hydrogen-bond persistence times are on the order of picoseconds which is
much smaller than characteristic time for particle motion.
%\cite{MaGa13}. 
Thus we assume $u$ minimizes $F[u]$ for all times. Assuming appropriate
conditions on $f(u)$,
% (\cite{evans10}, \S 8.2),
$u$ satisfies the Euler-Lagrange equation
\begin{alignat}{3}
  \label{eq:SL}
  -\rho^2 \Delta u + \tfrac{1}{2}f'(u) &= 0, && \xx \in \Omega, \\
  u &= g, && \xx \in \bd\Omega, \\
  u &\rightarrow 0, \qquad&& |\xx| \rightarrow \infty.
\end{alignat}
Equation~\eqref{eq:SL} is solved with a boundary integral equation
method. The boundary condition $g$ is a material label that is
transported with the particle.

@@

Distinct morphologies can be obtained from 
the HAP model by shifting the boundary condition $g(\xx)$.
Consider the linear case where $f(u) = u^2$.
This choice makes \eqref{eq:SL} a boundary value
problem for the screened-Laplace equation
and the solutions have a boundary layer structure that decays to $0$ in the
bulk with the decay length $\rho$.
We consider three kinds of boundary conditions
on particle $\Gamma_i$:
\begin{equation}
  \label{eq:bcs}
  \begin{tabular}{c|c|c}
     \text{(i)} & \text{(ii)} & \text{(iii)} \\
    \hline
    \rule{0pt}{4ex} 
      $g(\mathbf{x}) = \displaystyle \frac{1+\cos (\theta_i(\xx))}{\sqrt{3\pi r}}$
    & $g(\mathbf{x}) = \displaystyle \frac{2+\cos (\theta_i(\xx))}{\sqrt{9\pi r}}$
    & $g(\mathbf{x}) = \displaystyle \frac{\cos (\theta_i(\xx))}{\sqrt{\pi r}}$
\end{tabular}
\end{equation}
The number $\theta_i(\xx)$ is the angle formed by the position $\xx$,
the particle center $\aa_i$, and the particle director $\dd_i$.% (Figure
\ref{fig:flow_map}).
The normalizations e.g., $(\pi r)^{-1/2}$, provide a uniform surface
energy $\int_{\Gamma_i} g^2 \,ds = 1$ for circular particles of radius
$r$. The cases (ii) and (iii) are obtained by applying a vertical shift
and scaling to case (i).  Using this setup, we simulate the dynamics of
60 particles with one set of random initial positions and orientations
as shown in Figure~\ref{fig:relax}(a)
